% !TeX root = ../main.tex

\begin{achievements}

  \begin{theachievements}[已发表论文]
    \item \textbf{Shibo Liu}, Ligang Liu, Xiao-Ming Fu. Closed-form Generalized Winding Numbers of Rational Parametric Curves for Robust Containment Queries. ACM Transactions on Graphics (SIGGRAPH), 44(4), 2025.（第三章）
    \item \textbf{Shibo Liu}, Yang Ji, Jia-Peng Guo, Ligang Liu, Xiao-Ming Fu. Smooth Bijective Projection in a High-order Shell. ACM Transactions on Graphics (SIGGRAPH), 43(4), 2024.（第四章）
    \item \textbf{Shibo Liu}, Tielin Dai, Ligang Liu, Xiao-Ming Fu. Closed-form Cauchy Coordinates and Their Derivatives for 2D High-order Cages. Proceedings of the SIGGRAPH Asia 2025 Conference Papers (SIGGRAPH Asia), 2025.（第五章）
    \item \textbf{Shibo Liu}, Tielin Dai, Ligang Liu, Xiao-Ming Fu. Polynomial 2D Biharmonic Coordinates for High-order Cages. ACM Transactions on Graphics (SIGGRAPH), 44(4), 2025.（第六章）
    \item Zirui Wang*, \textbf{Shibo Liu}*, Ligang Liu, Qiang Zou, Xiao-Ming Fu. Computing Smooth Preferred Feed Direction Fields with High Material Removal Rates for Efficient CNC Tool Paths. Computer-Aided Design, 164: 103591, 2023. (*Joint first authors)
    \item Wei Du, \textbf{Shibo Liu}, Jia-Peng Guo, Ligang Liu, Xiao-Ming Fu. Robust and Efficient Preservation of High-order Continuous Geometric Validity. IEEE Transactions on Visualization and Computer Graphics, 2025.
    \item Xiongyu Wu, \textbf{Shibo Liu}, Xiao-Ming Fu. Polynomial 3D Green Coordinates and their Derivatives for Linear Cages. Computers \& Graphics, 2025.
    \item Zhaobin Huang, \textbf{Shibo Liu}, Xiao-Ming Fu. High-order Shape Interpolation. Computer-Aided Geometric Design (GMP), 2024.
    \item Yang Ji, \textbf{Shibo Liu}, Jia-Peng Guo, Jian-Ping Su, Xiao-Ming Fu. Evolutionary Multi-objective High-order Tetrahedral Mesh Optimization. Computer-Aided Geometric Design (GMP), 2024.
    \item Jinlin Yang, \textbf{Shibo Liu}, Shuangming Chai, Ligang Liu, Xiao-Ming Fu. Precise High-order Meshing of 2D Domains with Rational B\'{e}zier Curves. Computer Graphics Forum (SGP), 41(5), 2022.
  \end{theachievements}


\end{achievements}
